---
title: "CASPER Meta-Analysis Documentation"
author: "Nick Cardamone"
date: '2023-08-09'
categories: R
tags:
- R Markdown
- meta analysis
- implementation science
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```


### DistillerSR options:
* Advanced Options: Hide Empty Columns, Merge Sets by Key, Compress checkboxes to one column, "Merge Data and duplicate single forms to repeating forms", 
* Data criteria: user = cardamone, 
* Reference display options: display author and title
* Report settings: limit to label = "RCT" & NOT "throwaway"
* "study char": Study char + determinants + outcomes
* "icc_cov": Source + Covariate R-Sq
* "sample_size": Source + Conditions
* "effect_size": Source + Effect Size

```{r, include=FALSE}
library(tidyverse)
library(readxl)
library(dplyr)
library(metafor)
library(ggplot2)

#setwd("C:\\Users\\nickcardamone\\Downloads\\")
study_characteristics <- read_xlsx("study_char_2023-08-08-18-43-39.xlsx") # Study / Strategy / Outcome
sample_size <- read_xlsx("sample_size_2023-08-08-18-43-17.xlsx")  # Study / Outcome / Source
icc_cov <- read_xlsx("icc_cov_2023-08-08-18-42-53.xlsx") # Study / Outcome / Source
effect_size <- read_xlsx("effect_size_2023-08-08-18-43-02.xlsx") # Study / Outcome / Source / Contrast
```

### Only keep entries filled in by Nick
```{r}
# Remove irrelevant variables: e.g. all notes, comments, info: also collapse the analysis type variable. 
study_characteristics <- study_characteristics %>% filter(str_detect(Characteristics_k, "Nick") == T) %>% select(-ends_with("notes"), -ends_with("comment"), -ends_with("info"), -Level, -User)
sample_size <- sample_size %>% filter(str_detect(Source_k, "Nick") == T) %>% select(-ends_with("notes"), -ends_with("comment"), -ends_with("info"), -Level, -User)
icc_cov <- icc_cov %>% filter(str_detect(Source_k, "Nick") == T) %>% select(-ends_with("notes"), -ends_with("comment"), -ends_with("info"), -Level, -User) %>% tidyr::unite("analysis_type", c(analysis_type, measure_type_ep), sep= "_", remove = T, na.rm = T)
effect_size <- effect_size %>% filter(str_detect(Source_k, "Nick") == T) %>% select(-ends_with("notes"), -ends_with("comment"), -ends_with("info")) %>% tidyr::unite("analysis_type", c(analysis_type, measure_type_ep), sep= "_", remove = T, na.rm = T)

```
```{r}
# Make the number of time points a numeric variable -- if it's not a longitudinal study just change the number of time points to 1.
effect_size <- effect_size %>% mutate(
         num_timepoints = if_else(!is.na(num_timepoints_standard), as.numeric(num_timepoints_standard), 
                                  if_else(!is.na(num_timepoints_nonstandard), as.numeric(num_timepoints_nonstandard), 
                                          if_else(analysis_type != "long", 1, NA)))) %>% select(-measure_type_long, -num_timepoints_standard, -num_timepoints_nonstandard, -Level, -User, -cov_applicable)


# Remove "NR"
study_characteristics[study_characteristics == "NR"] <- NA
sample_size[sample_size == "NR"] <- NA
icc_cov[icc_cov == "NR"] <- NA
effect_size[effect_size == "NR"] <- NA
```

### Study Characteristics
* Outcomes
* Implementation Strategies
* Study Metadata
```{r}
outcomes <- study_characteristics %>% select(Refid, Outcomes_k, dv_name, dv_outcome, dv_measure_approach)
# We're only taking variables at the study level for the implementation strategies and metadata datasets so

imp_strategies <- study_characteristics %>% select(Refid, IVs_k, imp1_name:control_target) %>% distinct() 
metadata <- study_characteristics %>% select(Refid:imps_rand_1) %>% distinct() 

#Make dummy variables for randomization level

metadata$rand_L1 <- if_else(str_detect(as.character(metadata$imps_rand_1), "1"), 1, 0)
metadata$rand_L2 <- if_else(str_detect(as.character(metadata$imps_rand_1), "2"), 1, 0)
metadata$rand_L3 <- if_else(str_detect(as.character(metadata$imps_rand_1), "3"), 1, 0)
metadata$rand_L4 <- if_else(str_detect(as.character(metadata$imps_rand_1), "4"), 1, 0)
```
```{r}
# Pivot longer so that 1 row = 1 condition (nested within studies.)
names <- imp_strategies %>% pivot_longer(cols = c("imp1_name", "imp2_name","imp3_name", "control_name"), names_to = "comparator", values_to = "name", names_pattern = "(.*)_name") %>% select(Refid, IVs_k, comparator, name)
eric <- imp_strategies %>% pivot_longer(cols = ends_with("eric"), names_to = "comparator", values_to = "strategies", names_pattern = "(.*)_eric") %>% select(Refid, comparator, strategies)
target <- imp_strategies %>% pivot_longer(cols = c("imp1_target", "imp2_target","imp3_target", "control_target"), names_to = "comparator", values_to = "target", names_pattern = "(.*)_target") %>% select(Refid, comparator, target)

```
```{r}
# Mash the columns back together to make a tidied dataset for implementation strategies.

imp_strategies <- data.frame(names, eric = eric$strategies, target = target$target)

imp_strategies <- imp_strategies %>% filter(!is.na(name))

imp_strategies$cond_num <- ave(imp_strategies$comparator, imp_strategies$Refid, FUN = seq_along)
imp_strategies$target <- str_to_lower(imp_strategies$target)

imp_strategies <- imp_strategies %>% separate(target, into = c("target1", "target2"), sep = ",")
imp_strategies <- imp_strategies %>% separate(target1, into = c("target1", "target1_detail"), sep = " : ")
imp_strategies <- imp_strategies %>% separate(target2, into = c("target2", "target2_detail"), sep = " : ")
```
** One row per study ** 
```{r}
imp_strategies_wide <- imp_strategies %>% select(Refid, IVs_k, name, eric, target1, target2, cond_num) %>% pivot_wider(names_from = "cond_num", values_from = c("name", "eric", "target1", "target2"))
```


### Sample Size
```{r}
## Load sample size (Multiple sets of values per DV)
sample_size <- sample_size %>% drop_na(data_source)

#sample_size <- sample_size %>% filter(!is.na(cond_num) & !is.na(data_source))
##### Pivot wider to have unique columns for sample size at each level.

sample_size <- sample_size %>% drop_na(cond_num)
sample_size <- sample_size %>% dplyr::select(Source_k, cond_num, L1_condition_N, L2_condition_N, L3_condition_N, L4_condition_N) #%>% 

# Pivot wider 
sample_size <- reshape(
  merge(sample_size,
        expand.grid(
          Source_k = unique(sample_size$Source_k),
          cond_num = 1:3
        ),
        all = TRUE
  ),
  direction = "wide",
  idvar = "Source_k",
  timevar = "cond_num"
)

head(sample_size)
```

### ICC and COVARIATE R-SQ:
```{r}
# Fix ICC values:
# If L1 variance and L2 variance are in the old L1/L2 variance fields, copy them onto the new fields.
# Drop the + from the "+3" in the num_levels variable so it can be numeric.
# From the PI provided data, just compute the ICC at each level from the VCEs so it's standardized, if it's from the paper leave it alone.
icc_cov <- icc_cov %>% dplyr::mutate(L1_variance_3 = if_else(is.na(L1_variance_3), as.numeric(L1_variance_2), as.numeric(L1_variance_3)),
                                     L2_variance_3 = if_else(is.na(L2_variance_3), as.numeric(L2_variance_2), as.numeric(L2_variance_3)),
                                     num_levels = as.numeric(gsub("\\+", "", `num_levels`)),
                                     ICC_2 = if_else(num_levels == 2 & data_source == "PI", as.numeric(L2_variance_3)/(as.numeric(L1_variance_3)+as.numeric(L2_variance_3)),
                                                     if_else(num_levels == 3 & data_source == "PI", as.numeric(L2_variance_3)/(as.numeric(L1_variance_3)+as.numeric(L2_variance_3)+as.numeric(L3_variance_3)),
                                                             if_else(num_levels == 4 & data_source == "PI", as.numeric(L2_variance_3)/(as.numeric(L1_variance_3)+as.numeric(L2_variance_3)+as.numeric(L3_variance_3)+as.numeric(L4_variance_3)), as.numeric(ICC_2)))),
                                     ICC_3 = if_else(num_levels == 3 & data_source == "PI", as.numeric(L3_variance_3)/(as.numeric(L1_variance_3)+as.numeric(L2_variance_3)+as.numeric(L3_variance_3)),
                                                     if_else(num_levels == 4 & data_source == "PI",
                                                             as.numeric(L3_variance_3)/(as.numeric(L1_variance_3)+as.numeric(L2_variance_3)+as.numeric(L3_variance_3)+as.numeric(L4_variance_3)), as.numeric(ICC_3))),
                                     ICC_4 = if_else(num_levels == 4 & data_source == "PI", as.numeric(L4_variance_3)/(as.numeric(L1_variance_3)+as.numeric(L2_variance_3)+as.numeric(L3_variance_3)+as.numeric(L4_variance_3)),
                                                     as.numeric(ICC_4)))

```

## Covariate R-squared
```{r}
# Substitute null model VCE at each level if a value isn't already there.
icc_cov <- icc_cov %>% dplyr::mutate(NULL_VCE = if_else(!is.na(NULL_VCE), as.numeric(NULL_VCE), 
                                                        if_else(level_VCE == 1, as.numeric(L1_variance_3), 
                                                                if_else(level_VCE == 2, as.numeric(L2_variance_3),
                                                                        if_else(level_VCE == 3, as.numeric(L3_variance_3),
                                                                                if_else(level_VCE == 4, as.numeric(L4_variance_3), NA))))))

icc_cov <- icc_cov %>% dplyr::mutate(
  ## 1 - (PRETEST VCE/ NULL VCE)
  pretest_covR = 1-as.numeric(pretest_cov_VCE)/as.numeric(NULL_VCE), 
  ## 1 - (DEMO VCE / NULL VCE)
  demo_covR = 1-as.numeric(demo_cov_VCE)/as.numeric(NULL_VCE), 
  ## 1 - (FULL VCE / NULL VCE)
  covR = 1-as.numeric(full_VCE)/as.numeric(NULL_VCE))

```
```{r}
cov <- icc_cov %>% select(Source_k, level_VCE, covR, demo_covR, demo_cov, pretest_covR, L1_variance_3, L2_variance_3, L3_variance_3, L4_variance_3, ICC_2, ICC_3, ICC_4) %>% pivot_wider(names_from = level_VCE, values_from = c(covR, demo_covR, demo_cov, pretest_covR))
```


### EFFECT SIZE
```{r}
#effect_size <- effect_size %>% filter(d_adj != "adj" | is.na(d_adj))
eff_ss <- left_join(effect_size, sample_size, "Source_k")
eff_ss <- eff_ss %>% select(-L1_variance_3, -L2_variance_3, -L3_variance_3, -L4_variance_3, -ICC_1, -ICC_2, -ICC_3, -ICC_4, -L1_variance_2, -L2_variance_2,)
eff_ss <- left_join(eff_ss, cov, "Source_k")

## Drop if contrast is NA
eff_ss <- eff_ss %>% drop_na(d_contrast)

## Set contrast sample sizes:
eff_ss <- eff_ss %>% mutate(L1_condition_N_1 = if_else(d_contrast == "2v3", L1_condition_N.2, L1_condition_N.1),
                            L1_condition_N_2 = if_else(d_contrast == "1v2", L1_condition_N.2, L1_condition_N.3),
                            L2_condition_N_1 = if_else(d_contrast == "2v3", L2_condition_N.2, L2_condition_N.1),
                            L2_condition_N_2 = if_else(d_contrast == "1v2", L2_condition_N.2, L2_condition_N.3),
                            L3_condition_N_1 = if_else(d_contrast == "2v3", L3_condition_N.2, L3_condition_N.1),
                            L3_condition_N_2 = if_else(d_contrast == "1v2", L3_condition_N.2, L3_condition_N.3),
                            L4_condition_N_1 = if_else(d_contrast == "2v3", L4_condition_N.2, L4_condition_N.1),
                            L4_condition_N_2 = if_else(d_contrast == "1v2", L4_condition_N.2, L4_condition_N.3))

```
```{r}
## Time transformations
eff_ss <- eff_ss %>% dplyr::mutate(duration = if_else(standard_time_interval == "Yes", as.numeric(measurement_interval_num) * (num_timepoints-1), 
                                                      if_else(num_timepoints ==2, as.numeric(gsub("[^0-9.-]", "", follow_up1)), 
                                                              if_else(num_timepoints ==3, as.numeric(gsub("[^0-9.-]", "", follow_up2)),
                                                                      if_else(num_timepoints ==4, as.numeric(gsub("[^0-9.-]", "", follow_up3)), 3)))),
                                   follow_up1 = if_else(standard_time_interval == "Yes", as.numeric(measurement_interval_num), 
                                                        as.numeric(gsub("[^0-9.-]", "", follow_up1))))
```
```{r}
## Raw SD transformation
eff_ss <- eff_ss %>% dplyr::mutate(num_levels = as.numeric(gsub("\\+", "", `num_levels`)),
                                   d_raw_SD = if_else(!is.na(d_raw_SD), as.numeric(d_raw_SD),
                                                      if_else(num_levels == 4, sqrt(as.numeric(L1_variance_3) + as.numeric(L2_variance_3) + as.numeric(L3_variance_3) + as.numeric(L4_variance_3)),
                                                              if_else(num_levels == 3, sqrt(as.numeric(L1_variance_3) + as.numeric(L2_variance_3) + as.numeric(L3_variance_3)),
                                                                      if_else(num_levels == 2, sqrt(as.numeric(L1_variance_3) + as.numeric(L2_variance_3)), NA))))) 
## Effect size transformations
eff_ss <- eff_ss %>% dplyr::mutate(
  d_cont = as.numeric(reg_coef)/as.numeric(d_raw_SD), # endpoint analysis or categorical time
  d_binary = as.numeric(reg_coef) * sqrt(3)/pi, #it spits out a logit and its converted
  ## Time-varying effect size
  d_long_cat = as.numeric(reg_coef_tx)/as.numeric(d_raw_SD), # Categorical time reg_coef is already multiplied by the duration. 
  d_long_piecewise = (as.numeric(reg_coef_tx)*follow_up1)/as.numeric(d_raw_SD), # Input directly into distillerSR
  d_long_linear = (as.numeric(reg_coef_tx)*as.numeric(duration))/as.numeric(d_raw_SD),
  d_long_quadratic = ((as.numeric(reg_coef_tx)*as.numeric(duration)) + ((as.numeric(reg_coef_tx_q)*as.numeric(duration)^2)))/as.numeric(d_raw_SD),
  ## Extract effect size from t-value or p-value (Need to add bias correction)
  d_t_test =  if_else(d_CR_type == "t", as.numeric(d_CR) * sqrt(1/as.numeric(L1_condition_N_1) + 1/as.numeric(L1_condition_N_2)), NA),
  d_from_pval =  pt(as.numeric(gsub("[^0-9.-]", "", d_pval))/2, 100) * sqrt(1/as.numeric(L1_condition_N_1) + 1/as.numeric(L1_condition_N_2)),
  d_author = as.numeric(gsub("[^0-9.-]", "", d_author)))
```
### COMPONENTS FOR VARIANCE ESTIMATES
```{r}
eff_ss <- eff_ss %>% 
  mutate(tot_v2 = if_else(num_levels == 2, as.numeric(L1_variance_3)+as.numeric(L2_variance_3), NA), # Total variance at level 2
         tot_v3 = if_else(num_levels == 3, as.numeric(L1_variance_3)+as.numeric(L2_variance_3)+as.numeric(L3_variance_3), NA), # Total variance at level 3
         tot_v4 = if_else(num_levels == 4, as.numeric(L1_variance_3)+as.numeric(L2_variance_3)+as.numeric(L3_variance_3)+as.numeric(L4_variance_3), NA), # Total variance at level 4

         L1_ss = if_else(is.na(L1_ss), as.numeric(L1_condition_N_1) + as.numeric(L1_condition_N_2), as.numeric(L1_ss)), # Add L1 conditions sample size together to make L1 sample size, if L1 sample size isn't already there.
         L2_ss = if_else(is.na(L2_ss), as.numeric(L2_condition_N_1) + as.numeric(L2_condition_N_2), as.numeric(L2_ss)), # .
         L3_ss = if_else(is.na(L3_ss), as.numeric(L3_condition_N_1) + as.numeric(L3_condition_N_2), as.numeric(L3_ss)), # .
         L4_ss = if_else(is.na(L4_ss), as.numeric(L4_condition_N_1) + as.numeric(L4_condition_N_2), as.numeric(L4_ss)), 
         vi_r2_1 = 4*covR_1*(1-covR_1)^2 / L1_ss, # Variance of COV-R^2 at L1
         vi_r2_2 = 4*covR_2*(1-covR_2)^2 / L2_ss,
         vi_r2_3 = 4*covR_3*(1-covR_3)^2 / L3_ss,
        clus_1_2 = L1_ss/L2_ss, # Average number of L1 obs in L2 clusters.
        #clus_1_3 = L1_ss/L3_ss, # Average number of L1 obs in L3 clusters.
        clus_2_3 = L2_ss/L3_ss, # Average number of L2 obs in L3 clusters.
        clus_3_4 = L3_ss/L4_ss, # Average number of L3 obs in L4 clusters.
        v2 = as.numeric(L2_variance_3_se)^2, # Variance of L2 Variance
        v3 = as.numeric(L3_variance_3_se)^2, # Variance of L3 Variance
        v4 = as.numeric(L4_variance_3_se)^2, # Variance of L4 Variance
        vi_icc_2 = if_else(num_levels == 2, (2*(1-ICC_2)^2 * (1+(clus_1_2-1)*ICC_2)^2)/(clus_1_2*(clus_1_2-1)*(L2_ss-1)), # Variance of ICC @ L2
                       if_else(num_levels == 3, (((clus_2_3*(1-ICC_2)^2 + 2*ICC_2*(1-ICC_2))*v2)/(clus_2_3*tot_v3^2)) + ((ICC_2^2 * v3)/tot_v3^2),
                               if_else(num_levels == 4, ((clus_3_4*clus_2_3^2*(1-ICC_2)^2+2*clus_3_4*clus_2_3*ICC_2*(1-ICC_2)+2*ICC_2^2)*v2)/(clus_3_4*clus_2_3^2*tot_v4^2)+((clus_3_4-2)*ICC_2^2*v3)/(clus_3_4*tot_v4^2)+(ICC_2^2*v4)/tot_v4^2, NA))),
                       
        vi_icc_3 = if_else(num_levels == 3, (((clus_2_3*(ICC_3)^2 + 2*ICC_3*(1-ICC_3))*v2)/(clus_2_3*tot_v3^2)) + (((1-ICC_3)^2 * v3)/tot_v3^2),
                           
                         if_else(num_levels == 4, (((clus_3_4*clus_2_3^2*ICC_3^2 + 2*(clus_3_4*clus_2_3 - 1)*ICC_3*(1-ICC_3))*v2)/(clus_3_4*clus_2_3^2*tot_v4^2))+ ((((clus_3_4*(1-ICC_3)^2)+(2*ICC_3*(1-ICC_3)))*v3)/(clus_3_4*tot_v4^2))+((ICC_3^2*v4)/tot_v4^2), NA)),
        
        vi_icc_4 = if_else(num_levels == 4, (((clus_3_4*clus_2_3*(clus_2_3 - 2)*ICC_4^2 - 2*ICC_4*(1-ICC_4))*v2)/(clus_3_4*clus_2_3^2*tot_v4^2))+(((clus_3_4*ICC_4^2+2*ICC_4*(1-ICC_4))*v3)/(clus_3_4*tot_v4^2))+((1-ICC_4)^2*v4)/tot_v4^2, NA)) # Variance of ICC @ L3 
```

### PIVOT LONGER TO CREATE EFFECT SIZE PARAMETER COMPONENTS:

```{r}
eff_ss_long <- eff_ss %>% pivot_longer(c("d_author", "d_binary", "d_cont", "d_long_piecewise", "d_long_cat", "d_long_linear", "d_long_quadratic", "d_t_test", "d_from_pval"), names_to = "dtype", values_to = "dval") #%>% drop_na(dval)

eff_ss_long <- eff_ss_long %>% 
  mutate(analysis_type = if_else(str_detect(analysis_type, "binary") == T, "binary", 
                                                                      if_else(str_detect(analysis_type, "cont") == T, "cont",
                                                                              if_else(analysis_type == "ep", "cont", "long"))),
         analysis_match = if_else(dtype == "d_cont" & analysis_type == "cont" & data_source == "PI", 1, 
                                  if_else(dtype == "d_binary" & analysis_type == "binary" & data_source == "PI", 1, 
                                    if_else(dtype == "d_long_cat" & time_modeled == "cat", 1, 
                                     if_else(dtype == "d_long_piecewise" & time_modeled == "piecewise", 1,
                                          if_else(dtype == "d_long_linear" & time_modeled == "linear", 1,
                                                  if_else(dtype == "d_long_quadratic" & time_modeled == "quad",  1, 
                                                          if_else(dtype == "d_author" & data_source == "Paper" & analysis_type == "cont", 1,
                                                                  if_else(dtype == "d_from_pval" & data_source == "Paper" & analysis_type == "cont", 1,
                                                                          if_else(dtype == "d_t_test" & data_source == "Paper"& analysis_type == "cont", 1, 0))))))))),
    num_levels = as.numeric(gsub("\\+", "", `num_levels`)),
    vi = if_else(dtype == "d_cont" & num_levels == 2, (as.numeric(reg_coef_se)^2/tot_v2) + (as.numeric(reg_coef)^2 * as.numeric(L2_variance_3_se)^2)/(4*(tot_v2)^3),
                 if_else(dtype == "d_cont" & num_levels == 3, (as.numeric(reg_coef_se)^2/tot_v3) + (as.numeric(reg_coef)^2 * (as.numeric(L2_variance_3_se)^2 + as.numeric(L3_variance_3_se)^2))/(4*tot_v3^3),
                         if_else(dtype == "d_cont" & num_levels == 4, (as.numeric(reg_coef_se)^2/tot_v4) + (as.numeric(reg_coef)^2 * (as.numeric(L2_variance_3_se)^2 + as.numeric(L3_variance_3_se)^2 + as.numeric(L4_variance_3_se)^2))/(4*tot_v4^3),
                         if_else(dtype == "d_long_linear" | dtype == "d_long_quadratic" | dtype == "d_long_piecewise" | dtype == "d_long_cat", as.numeric(reg_coef_tx_se)^2 * (as.numeric(dval)/as.numeric(reg_coef_tx))^2, 
                                                 if_else(dtype == "d_binary", 3*as.numeric(reg_coef_se)^2/pi^2, NA)))))) %>% filter(analysis_match == 1) %>% select(Refid:software, L1_ss:num_levels, d_contrast:d_adj, L1_variance_3:L4_variance_3, follow_up1, duration, analysis_type, time_modeled, dtype:vi)


```

## META-ANALYZE:

### ICC AND COV R^2
 * Analyzed at the outcome level.
 
```{r}
icc_cov_meta <- eff_ss %>% select(Refid, Source_k, data_source:L3_ss, L1_analysis_name, L2_analysis_name, L3_analysis_name, L4_analysis_name, L4_ss, num_levels, L1_variance_3_se, L2_variance_3_se, L3_variance_3_se, L4_variance_3_se, L1_variance_3:pretest_covR_2, tot_v2:vi_icc_4)
icc_cov_meta <- icc_cov_meta %>% separate(col = Source_k, into = c("study", "determinant", "dv_name", "dv_source"), sep = "\\|") %>% select(-dv_source)
icc_cov_meta <- left_join(icc_cov_meta, outcomes, c("Refid", "dv_name"))
metadata <- metadata %>% select(Refid, Author, hybrid_type:rand_L4)
icc_cov_meta <- left_join(icc_cov_meta, metadata, "Refid")


icc_meta_pi <- icc_cov_meta %>% filter(data_source == "PI") %>% distinct() %>% select(Author, Refid, dv_name, study, analysis_type, dv_outcome, dv_measure_approach, L1_name, L2_name, L3_name, L1_analysis_name, L2_analysis_name, L3_analysis_name, L4_analysis_name, num_levels, L1_variance_3, L2_variance_3, L3_variance_3, L4_variance_3, L1_variance_3_se, L2_variance_3_se, L3_variance_3_se, L4_variance_3_se, L1_ss, L2_ss, L3_ss, L4_ss, clus_1_2, clus_1_2, ICC_2, vi_icc_2, ICC_3, vi_icc_3, ICC_4, vi_icc_4, covR_1, vi_r2_1, covR_2, vi_r2_2)

cov_meta_pi <- icc_cov_meta %>% filter(data_source == "PI") %>% distinct() %>% select(Author, Refid, dv_name, study, analysis_type, dv_outcome, dv_measure_approach, L1_name, L2_name, L3_name, L1_analysis_name, L2_analysis_name, L3_analysis_name, L4_analysis_name, num_levels, L1_variance_3, L2_variance_3, L3_variance_3, L4_variance_3, L1_variance_3_se, L2_variance_3_se, L3_variance_3_se, covR_1, vi_r2_1, covR_2, vi_r2_2)

#icC_cov_meta_paper <- icc_cov_meta %>% filter(data_source == "Paper") %>% distinct() %>% select(Author, Refid, dv_name, study, analysis_type, dv_outcome, L1_name, L2_name, L3_name, L4_name, num_levels, L1_variance_3, L2_variance_3, L3_variance_3, L4_variance_3, L1_variance_3_se, L2_variance_3_se, L3_variance_3_se, L4_variance_3_se, L1_ss, L2_ss, L3_ss, L4_ss, clus_1_2, clus_1_3, clus_1_2, ICC_2, vi_icc_2, ICC_3, vi_icc_3, covR_1, vi_r2_1, covR_2, vi_r2_2)

```
```{r}
icc_meta_pi <- icc_meta_pi %>% 
  mutate(L1_name = if_else(is.na(L1_name), L1_analysis_name, L1_name),
         L2_name= if_else(is.na(L2_name), L2_analysis_name, L2_name),
         L3_name= if_else(is.na(L3_name), L3_analysis_name, L3_name),
         L4_name= L4_analysis_name, # Right now, L4_name doesn't exist because there isn't a variable with data at the study characteristics level, only at the outcome level because of the two weird cases where we have differing model structures depending on the outcome in Epstein and Cara Lewis.
         
         analysis_type = if_else(str_detect(analysis_type, "binary") == T, "binary", 
                                                                      if_else(str_detect(analysis_type, "cont") == T, "cont",
                                                                              if_else(analysis_type == "ep", "cont", "long"))),
         longitudinal = if_else(analysis_type == "long", 1, 0),
         outcome_type = if_else(dv_outcome == "symptoms" | dv_outcome == "functioning", "clinical", "implementation"),
         measurement_approach = if_else(dv_measure_approach == "provider" | dv_measure_approach == "participant", "self_report", 
                                        if_else(is.na(dv_measure_approach), NA, "coded/recorded")))

icc_meta_pi <- icc_meta_pi %>% pivot_longer(c(ICC_2, ICC_3, ICC_4), names_to = "level_ICC", values_to = "ICC") %>% 
  mutate(analysis_index = paste0(analysis_type, num_levels, level_ICC)) %>% mutate(cluster_level = if_else(level_ICC == "ICC_2", L2_name,
                                                                                                           if_else(level_ICC == "ICC_3", L3_name, NA)), 
                                                                                   ICC_vi = if_else(level_ICC == "ICC_2", vi_icc_2,
                                                                                                    if_else(level_ICC == "ICC_3", vi_icc_3, 
                                                                                                            if_else(level_ICC == "ICC_4", vi_icc_4, NA))))
```

```{r}
# Make the non-longitudinal, first-cluster data set.
icC_cov_meta_pi_L2 <- icc_meta_pi %>% filter(analysis_index == "long4ICC_3" | analysis_index == "long3ICC_3" | analysis_index == "cont3ICC_2" | analysis_index == "binary3ICC_2" | analysis_index == "cont2ICC_2" | analysis_index == "binary2ICC_2") %>% filter(!is.na(ICC))

# Make the non-longitudinal, second-cluster data set.

icC_cov_meta_pi_L3 <- icc_meta_pi %>% filter(analysis_index == "long4ICC_4" | analysis_index == "cont3ICC_3" | analysis_index == "binary3ICC_3")

# Make the longitudinal data set
icC_cov_meta_pi_long <- icc_meta_pi %>% filter(analysis_index == "long4ICC_2" | analysis_index == "long3ICC_2" | analysis_index == "long2ICC_2")

# Fix the observations of Epstein's 4-level variable.
#icC_cov_meta_pi_long[4, 8] <- "obs"
#icC_cov_meta_pi_long[4, 9] <- "patient"
#icC_cov_meta_pi_long[4, 10] <- "provider"
#icC_cov_meta_pi_long[4, 11] <- "site"
```
```{r}
summary(icC_cov_meta_pi_L2$ICC)
summary(icC_cov_meta_pi_L3$ICC)
summary(icC_cov_meta_pi_long$ICC)


IQR(icC_cov_meta_pi_L2$ICC)
IQR(icC_cov_meta_pi_L3$ICC)
IQR(icC_cov_meta_pi_long$ICC)
```
### Visualize ICC and COV R^2 Estimate
```{r, error = T}
meta_icc_L2 <- icC_cov_meta_pi_L2 %>% filter(!is.na(ICC_vi))
meta_icc_L3 <- icC_cov_meta_pi_L3 %>% filter(!is.na(ICC_vi)) 
meta_icc_long <- icC_cov_meta_pi_long %>% filter(!is.na(ICC_vi)) 

ma_model_2 <- rma.mv(yi = ICC, V = ICC_vi, random = ~ 1 | dv_name/study, data = meta_icc_L2)
ma_model_2i <- rma.mv(yi = ICC, V = ICC_vi, mods = as.factor(measurement_approach), random = ~ 1 | dv_name/study, data = meta_icc_L2) # Test for moderating force of measurement approach.

ma_model_3 <- rma.mv(yi = ICC, V = ICC_vi, random = ~ 1 | dv_name/study, data = meta_icc_L3)
ma_model_2_long <- rma.mv(yi = ICC, V = ICC_vi, random = ~ 1 | dv_name/study, data = meta_icc_long)

summary(ma_model_2)
summary(ma_model_3)
summary(ma_model_2_long)

forest(ma_model_2, slab = paste(gsub(",", "", str_sub(meta_icc_L2$Author, 1, 10)), str_sub(meta_icc_L2$dv_name, 1, 10), cluster_level, sep = ", "))
title("ICC, Non-longitudinal clusters L2")

forest(ma_model_3, slab = paste(gsub(",", "", str_sub(meta_icc_L3$Author, 1, 10)), str_sub(meta_icc_L3$dv_name, 1, 10), cluster_level, sep = ", "))
title("ICC, Non-longitudinal clusters L3")

forest(ma_model_2_long, slab = paste(gsub(",", "", str_sub(meta_icc_long$Author, 1, 10)), str_sub(meta_icc_long$dv_name, 1, 10), cluster_level, sep = ", "))
title("ICC, Longitudinal clusters")


clubSandwich::coef_test(ma_model_2, vcov = "CR2")# RVE using small-sample adjustment from Tipton and Pustejovsky (2015)
clubSandwich::coef_test(ma_model_3, vcov = "CR2")# RVE using small-sample adjustment from Tipton and Pustejovsky (2015)
clubSandwich::coef_test(ma_model_2_long, vcov = "CR2")# RVE using small-sample adjustment from Tipton and Pustejovsky (2015)


```
#### Mixed effects model
##### Account for clustering in the results, but don't meta-analyze
```{r}
library(lme4) # Mixed effects models
#lm(ICC ~ 1, data = icC_cov_meta_pi_L2)

m1 = lmer(ICC ~ 1 + (1 | Refid), data = icC_cov_meta_pi_L2) # Level 2

summary(lmer(ICC ~ outcome_type + (1 | Refid), data = icC_cov_meta_pi_L2)) # Level 2
summary(lmer(ICC ~ measurement_approach + (1 | Refid), data = icC_cov_meta_pi_L2)) # Level 2


m2 = lmer(ICC ~ 1 + (1 | Refid), data = icC_cov_meta_pi_L3) # Level 3
m3 = lmer(ICC ~ 1 + (1 | Refid), data = icC_cov_meta_pi_long) # Longitudinal

m1
stats::confint(m1, method="Wald")

m2
stats::confint(m2, method="Wald")

m3
stats::confint(m3, method="Wald")


```
#### Clustered Standard Errors
```{r}
library(sandwich) # Working with clustered covariances
library(miceadds) # AUtomated function to work with clustered-random errors
m1 = lm.cluster(ICC ~ 1, cluster = 'Refid', data = icC_cov_meta_pi_L2)
summary(lm.cluster(ICC ~ longitudinal, cluster = 'Refid', data = icC_cov_meta_pi_L2))
summary(lm.cluster(ICC ~ outcome_type, cluster = 'Refid', data = icC_cov_meta_pi_L2))
summary(lm.cluster(ICC ~ measurement_approach, cluster = 'Refid', data = icC_cov_meta_pi_L2))

m2 = lm.cluster(ICC ~ 1, cluster = 'Refid', data = icC_cov_meta_pi_L3)
m3 = lm.cluster(ICC ~ 1, cluster = 'Refid', data = icC_cov_meta_pi_long)
summary(lm.cluster(ICC ~ outcome_type, cluster = 'Refid', data = icC_cov_meta_pi_long))
summary(lm.cluster(ICC ~ measurement_approach, cluster = 'Refid', data = icC_cov_meta_pi_long))


m1
stats::confint(m1, method="Wald")

m2
stats::confint(m2, method="Wald")

m3
stats::confint(m3, method="Wald")
```

#### Plot ICC Estimates
```{r}
# I manually input the estimates into a separate Excel workbook.
#icc_est <- read_xlsx("ICC_estimates.xlsx")
library(ggplot2)

#icc_plot <- ggplot(data = icc_est, mapping = aes(y = analysis, x= estimate, color = est_type)) + geom_point(position = position_dodge(width = 1), aes(shape = analysis, size = n_studies), show.legend = F) + geom_linerange(aes(xmin = lowerbound, xmax = upperbound), position = position_dodge(width = 1), size = .8) + xlab("ICC Estiamte") + coord_flip()

#icc_plot
#ggsave("ICC_estimates_plot.png", icc_plot)
```



## COV R-SQUARED
```{r}
meta_r2_L2 <- cov_meta_pi %>% filter(!is.na(vi_r2_1) & vi_r2_1 > 0)
meta_r2_L3 <- cov_meta_pi %>% filter(!is.na(vi_r2_2) & vi_r2_2 > 0)
#meta_r2_L4 <- cov_meta_pi %>% filter(!is.na(vi_r2_3) & vi_r2_3 > 0)

## COV R-Sq

ma_model_4 <- rma.mv(yi = covR_1, V = vi_r2_1, random = ~ 1 | dv_name/Refid, data = meta_r2_L2)
summary(ma_model_4)

ma_model_5 <- rma.mv(yi = covR_2, V = vi_r2_2, random = ~ 1 | dv_name/Refid, data = meta_r2_L3)
summary(ma_model_5)

#ma_model_6 <- rma.mv(yi = covR_3, V = vi_r2_3, random = ~ 1 | dv_name/Refid, data = meta_r2_L4)
#summary(ma_model_6)

forest(ma_model_4, slab = paste(str_sub(meta_r2_L2$Author, 1, 10), str_sub(meta_r2_L2$dv_name, 1, 20), sep = ", "))
title("Covariate R-Squared, Level 2")

forest(ma_model_5, slab = paste(str_sub(meta_r2_L3$Author, 1, 10), str_sub(meta_r2_L3$dv_name, 1, 20), sep = ", "))
title("Covariate R-Squared, Level 3")

#forest(ma_model_6, slab = paste(str_sub(meta_r2_L3$Author, 1, 10), str_sub(meta_r2_L3$dv_name, 1, 20), sep = ", "))
#title("Covariate R-Squared, Level 4")
```

```{r}
#d_meta <- eff_ss_long %>% select(Refid, Source_k, d_contrast, data_source:L3_ss, reg_coef, reg_coef_se, d_adj, duration, dtype:vi)
d_meta <- eff_ss_long %>% separate(col = Source_k, into = c("study", "determinant", "dv_name", "dv_source"), sep = "\\|") %>% select(-dv_source)

## Create a variable that identifies if the calculated d value aligns with the analysis conducted.
d_meta <- d_meta %>% select(-Author, -Title) %>% mutate(d_tp = if_else(is.na(d_tp), 1, is.numeric(d_tp)),
                                                                       d_adj = if_else(is.na(d_adj), "unadj", d_adj))



```

```{r}
d_meta_wide <- d_meta %>% group_by(Refid, dv_name, d_adj, dtype) %>% summarise(dval = mean(dval, na.rm = T)) %>% pivot_wider(names_from = c(d_adj, dtype), values_from = dval) %>% ungroup()

d_meta_wide <- left_join(d_meta_wide, outcomes, c("Refid", "dv_name"))
d_meta_wide <- left_join(d_meta_wide, metadata, "Refid")
d_meta_wide <- left_join(d_meta_wide, imp_strategies_wide, c("Refid", "IVs_k"))

#write.csv(d_meta_wide, "d_meta_wide.csv", na="")

```


```{r}
# Join study characteristics dataset with effect size dataset.
d_meta <- left_join(d_meta, outcomes, c("Refid", "dv_name"))
d_meta <- left_join(d_meta, metadata, "Refid")
d_meta <- left_join(d_meta, imp_strategies_wide, c("Refid", "IVs_k"))


d_meta_wide <- d_meta %>% group_by(dv_name, data_source, d_adj, d_contrast) %>% slice(which.min(d_tp)) %>% pivot_wider(names_from = c(data_source, d_adj, d_contrast, dtype), values_from = dval)



```
```{r}
## Index the contrast metadata to the appropriate contrast.
d_meta <- d_meta %>% mutate(prim_name = if_else(d_contrast == "1v2" | d_contrast == "1v3" | d_contrast == "1v4", name_1, 
                                                if_else(d_contrast == "2v3" | d_contrast == "2v4", name_2, name_3)),
                            comparator_name = if_else(d_contrast == "1v4" | d_contrast == "2v4" | d_contrast == "3v4", name_4, 
                                                if_else(d_contrast == "1v3" | d_contrast == "2v3", name_3, name_2)), 
                            prim_eric = if_else(d_contrast == "1v2" | d_contrast == "1v3" | d_contrast == "1v4", eric_1, 
                                                if_else(d_contrast == "2v3" | d_contrast == "2v4", eric_2, eric_3)),
                            comparator_eric = if_else(d_contrast == "1v4" | d_contrast == "2v4" | d_contrast == "3v4", eric_4, 
                                                if_else(d_contrast == "1v3" | d_contrast == "2v3", eric_3, eric_2)),
                            prim_target1 = if_else(d_contrast == "1v2" | d_contrast == "1v3" | d_contrast == "1v4", target1_1, 
                                                if_else(d_contrast == "2v3" | d_contrast == "2v4", target1_2, target1_3)),
                            comparator_target1 = if_else(d_contrast == "1v4" | d_contrast == "2v4" | d_contrast == "3v4", target1_4, 
                                                         if_else(d_contrast == "1v3" | d_contrast == "2v3", target1_3, target1_2)),
                            prim_target2 = if_else(d_contrast == "1v2" | d_contrast == "1v3" | d_contrast == "1v4", target2_1,
                                                   if_else(d_contrast == "2v3" | d_contrast == "2v4", target2_2, target2_3)),
                            comparator_target2 = if_else(d_contrast == "1v4" | d_contrast == "2v4" | d_contrast == "3v4", target2_4,
                                                         if_else(d_contrast == "1v3" | d_contrast == "2v3", target2_3, target2_2))) %>% select(Refid:rand_L4, prim_name:comparator_target2) 


# Take only d values with a variance, group by outcome and only take the first time point
# If the outcome is symptoms, flip the sign of the d value.
meta_d <- d_meta %>% filter(dval < 3 & dval > -1) %>% group_by(dv_name, d_contrast) %>% slice(which.min(d_tp)) %>% mutate(dval = if_else(dv_outcome == "symptoms", dval*-1, dval))


```

```{r}
# Subtract implementation strategies from each other.
meta_d <- meta_d %>%
    mutate(
        prim_subtracted = map2(
            str_split(prim_eric, ","),
            str_split(comparator_eric, ","),
            ~ setdiff(.x, .y)
        ) %>% map_chr(~ paste0(.x, collapse = ";")) %>% str_trim(),
        comparator_subtracted = map2(
            str_split(comparator_eric, ","),
            str_split(prim_eric, ","),
            ~ setdiff(.x, .y)
        ) %>% map_chr(~ paste0(.x, collapse = ";")) %>% str_trim(),
        comparator_subtracted = if_else(comparator_subtracted == "NA", "Service as usual", comparator_subtracted),
        effect_size_type = if_else(comparator_subtracted == "Service as usual", "Service as usual",
                                   if_else(comparator_subtracted == "", "Enhanced vs. Standard", "Comparative Effectiveness"))
    )
# Split apart datasets into 3 distinct analytical datasets.

# Make paper dataset, we have 3 different types of "paper" d-values (t-test, p-value directly reported) for now I just took the minimum.
meta_d_paper <- meta_d %>% filter(data_source == "Paper") %>% group_by(dv_name, d_contrast) %>% slice(which.min(d_tp))
meta_d_service_as_usual <- meta_d %>% filter(effect_size_type == "Service as usual" & !is.na(vi))
meta_d_enhancedvstandard <- meta_d %>% filter(effect_size_type == "Enhanced vs. Standard" & !is.na(vi))
meta_d_compeff <- meta_d %>% filter(effect_size_type == "Comparative Effectiveness" & !is.na(vi))

```

### Visualize Effect Size Estiamte

```{r}
# PLOT FOREST PLOT OF d values from PAPER
library(ggh4x) #https://cjvanlissa.github.io/Doing-Meta-Analysis-in-R/robust-variance-estimation-1.html
meta_d_paper %>% ggplot(aes(x = dval, y = interaction(str_sub(dv_name, 1, 15), dv_outcome, str_sub(Author, 1, 8)))) + geom_point(shape = "square") + geom_vline(aes(xintercept = 0), alpha = 0.5) + scale_y_discrete(guide = "axis_nested")
```


## Strategy vs. Service as usual
```{r}

# Should we use robust variance estimation: https://www.tandfonline.com/doi/abs/10.1080/13645579.2016.1252189

ma_model_1 <- rma.mv(yi = dval, vi, random = ~ 1 | dv_name/Refid, data = meta_d_service_as_usual)
summary(ma_model_1)

forest(ma_model_1, slab = paste(str_sub(meta_d_service_as_usual$Author, 1, 10), str_sub(meta_d_service_as_usual$prim_name, 1, 10), str_sub(meta_d_service_as_usual$dv_name, 1, 20)))
title("Effect Size: Strategy vs. Service as usual")

funnel(ma_model_1)

clubSandwich::coef_test(ma_model_1, vcov = "CR2") # RVE using method from Tipton and Pustejovsky (2015)
```

## Enhanced Implementation Strategy vs. Standard Implementation Strategy:

```{r}
ma_model_2 <- rma.mv(yi = dval, vi, random = ~ 1 | dv_name/Refid, data = meta_d_enhancedvstandard)
summary(ma_model_2)

forest(ma_model_2, slab = paste(str_sub(meta_d_enhancedvstandard$Author, 1, 10), str_sub(meta_d_enhancedvstandard$prim_name, 1, 10), str_sub(meta_d_enhancedvstandard$dv_name, 1, 20)))
title("Effect Size: Enhanced Strategy vs. Stategy")

funnel(ma_model_2)

clubSandwich::coef_test(ma_model_2, vcov = "CR2") # RVE using method from Tipton and Pustejovsky (2015)

```

## Comparative Effectiveness:

```{r}
ma_model_3 <- rma.mv(yi = dval, vi, random = ~ 1 | dv_name/Refid, data = meta_d_compeff)
summary(ma_model_3)

forest(ma_model_3, cex=0.9, header=TRUE, top=2, slab = paste(str_sub(meta_d_compeff$Author, 1, 10), str_sub(meta_d_compeff$prim_name, 1, 10), str_sub(meta_d_compeff$comparator_name, 1, 10), str_sub(meta_d_compeff$dv_name, 1, 20)))
title("Effect Size: Comparative Effectiveness")

funnel(ma_model_3)
 
clubSandwich::coef_test(ma_model_3, vcov = "CR2")# RVE using method from Tipton and Pustejovsky (2015)

```
